Title Goes Here

### 2024-04-17 analysis/paper/paper.qmd
minor edit to methods

ggplot() +
  geom_smooth(data =  jobdata_method_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  scale_colour_brewer(palette = "Dark2") +
  guides(colour = guide_legend("Method\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")

>>>>

ggplot() +
  geom_smooth(data =  jobdata_method_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  guides(colour = guide_legend("Method\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")
